hbm_paper_results

### 2024-06-04 paper_replication_results.Rmd
plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, gdata, gtExtras)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")

@@

cent.tbl.pretty <- cent.tbl %>%
  mutate(comp = case_when(comp == "cf.gam_cf" ~ "ComBat-GAM vs ComBat w/o Covariates",
                          comp == "cf.gamlss_cf" ~ "ComBatLS vs ComBat w/o Covariates", 
                          comp == "cf.gamlss_cf.gam" ~ "ComBatLS vs ComBat-GAM",
                          comp == "cf.lm_cf" ~ "Linear ComBat vs ComBat w/o Covariates",
                          comp == "cf.lm_cf.gam" ~ "Linear ComBat vs ComBat-GAM",
                          comp == "cf.lm_cf.gamlss" ~ "Linear ComBat vs ComBatLS"),
         smaller_group = case_when(smaller_group == "cf" ~ "ComBat w/o Covariates",
                                   smaller_group == "cf.lm" ~ "Linear ComBat",
                                   smaller_group == "cf.gam" ~ "ComBat-GAM",
                                   smaller_group == "cf.gamlss" ~ "ComBatLS")) %>%
  rename(#"Pairwise Comparison"=comp,
         "Lower Errors" = smaller_group,
         "N Features" = n_sig,
         "% Features" = perc_tests)

cent.tbl.pretty %>%
  gt() %>% 
  #gt_theme_538() %>% 
tab_style(style = list(cell_fill(color = "gray95")),
    locations = cells_row_groups()) %>%
  fmt_percent(
    columns = "% Features",
    decimals = 2
  ) %>%
  tab_options(column_labels.font.weight = "bold") %>%
  tab_header(title = "Pairwise comparisons of ComBat methods' absolute centile errors for 208 brain features across 100 replications")
```

@@

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
cent.diffs.v.plot <- perm_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=dataset, y=mean_cent_abs.diff, color=perm), scale="count") +
  labs(y= "Mean Magnitude Centile Error", x = "ComBat Configurations") +
  scale_x_discrete(labels=c(dataset_names)) +
  # guides(fill=guide_legend(title="Sampling \nPermutation")) + 
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat configurations replicated 100x") +
  theme(legend.position="none")
cent.diffs.v.plot
ggsave(filename="figs/centile_violin.png", cent.diffs.v.plot, width=11, height=4.5, units="in")
```

@@

#look by feature type
sex_bias_hist_plt <- cent.subj.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss" | dataset == "cf.lm") %>%
  mutate(dataset = factor(dataset, levels = c("cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    perm = as.factor(sub("perm-0", "", perm))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=perm, fill=perm), alpha=0.3, position="identity", bins=40) +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat~dataset, scales="free_y", labeller = labeller(dataset = as_labeller(dataset_names))) +
  theme_linedraw(base_size=12) +
  theme(legend.position = "none") +
  labs(x="Male - Female Median Centile Errors", y="Number of Features") +
  ggtitle("Sex differences in median centile errors across 100 sampling replications")
ggsave(filename="figs/sex_bias_hist_plt.png", sex_bias_hist_plt)
```

@@

t.test.cent.sex.test.med <- cent.sex.test.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 11,
                           dataset=="cf.lm" ~ 11,
                           dataset=="cf.gam" ~ 10.5,
                           dataset=="cf.gamlss" ~ 6))

@@

sex_bias_density_plt <- cent.sex.test.med %>%
  dplyr::filter(dataset != "cf") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=y_pos),
              data = t.test.cent.sex.test.med.filt) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
```

@@

low_cent.sum <- perm_subj.df2_long %>%
  dplyr::filter(pheno_cat != "allpheno") %>%
  dplyr::filter(mean_centile < 0.20) %>%
  group_by(dataset, perm, pheno_cat) %>%
  summarise(
    male_ratio = sum(sex == "Male") / n(),
    female_ratio = sum(sex == "Female") / n()
  )

ext_cent.sum <- perm_subj.df2_long %>%
  dplyr::filter(pheno_cat != "allpheno") %>%
  dplyr::filter(mean_centile < 0.20 | mean_centile > 0.80) %>%
  group_by(dataset, perm, pheno_cat) %>%
  summarise(
    male_ratio = sum(sex == "Male") / n(),
    female_ratio = sum(sex == "Female") / n()
  )
```

@@

ext_cent.sum_raw <- ext_cent.sum %>%
  dplyr::filter(dataset == "raw" & perm=="perm-001")

@@

high_t_test.df <- lapply(split(high_cent.sum, high_cent.sum$pheno_cat), get_t_tests, raw_df=high_cent.sum_raw) %>% bind_rows()
low_t_test.df <- lapply(split(low_cent.sum, low_cent.sum$pheno_cat), get_t_tests, raw_df=low_cent.sum_raw) %>% bind_rows()
ext_t_test.df <- lapply(split(ext_cent.sum, ext_cent.sum$pheno_cat), get_t_tests, raw_df=ext_cent.sum_raw) %>% bind_rows()

#merge dfs
all_cent_sum.df <- gdata::combine(high_cent.sum, low_cent.sum, ext_cent.sum) %>%
  mutate(source = gsub("_cent.sum", "", source))
all_cent.sum_raw <- all_cent_sum.df %>%
  dplyr::filter(dataset == "raw" & perm=="perm-001")

all_t_test.df <- gdata::combine(high_t_test.df, low_t_test.df, ext_t_test.df) %>%
  mutate(source = gsub("_t_test.df", "", source))

@@

all_t_test.df <- full_join(all_t_test.df, y_pos.df)

#plots!
all_cent_sum.df %>%
  dplyr::filter(dataset != "raw") %>%
  ggplot(aes(x=dataset, y=female_ratio)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y") +
  geom_hline(data=all_cent.sum_raw, aes(yintercept=female_ratio), linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = max_val + 0.01),
              data = all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"),  name = "ComBat Configuration", labels=dataset_names) + 
  theme_linedraw()

cent_ext_list <- c(ext = ">80% and <20%", high = ">80%", low = "<20%")

all_cent_sum_boxplt.diff <- all_cent_sum.df_scaled %>%
  dplyr::filter(dataset != "raw" & dataset != "cf" & source != "ext") %>%
  mutate(source = factor(source, levels=c("low", "high", "ext"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio_diff)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(yintercept=0, linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = (y_pos)), nudge_y=.005,
               data = all_t_test.df[which(all_t_test.df$dataset != "cf" & all_t_test.df$source != "ext"),]) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  # scale_y_continuous(labels=function(x)x/all_t_test.df$female_ratio[which(raw_df$pheno_cat == pheno_cat)]) + 
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Female Bias", x = "Dataset")

all_cent_sum_boxplt_wtest <- all_cent_sum.df %>%
  dplyr::filter(dataset != "raw") %>%
  mutate(source = factor(source, levels=c("low", "high", "ext"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(data=all_cent.sum_raw, aes(yintercept=female_ratio), linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = max_val + 0.01),
              data = all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Proportion Female", x = "Dataset")

```

@@

```{r}
noext.cent.feat.t.test <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_t_tests_all_out.RDS"))
names(noext.cent.feat.t.test) <- n_perm_list
noext.cent.feat.t.test.df <- bind_rows(noext.cent.feat.t.test, .id="perm") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

@@

compare results
```{r}
noext.cent.t.test.df2 <- noext.cent.feat.t.test.df %>%
  mutate(full_df = 0)
cent.feat.t.test.df2 <- cent.feat.t.test.df %>%
  mutate(full_df = 1)

@@

@@

next.t.test.cent.sex.test.med <- noext.sex.testmed %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""))

@@

noext.sex.testmed %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=ifelse(t.test.cent.sex.test.med$dataset == "cf.gam", 10.2, 5.5)),
              data = next.t.test.cent.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
```

@@

```{r}
z.feat.t.test <- readRDS(paste0(data_path, "/full_featurewise_z_t_tests_all_out.RDS"))
names(z.feat.t.test) <- n_perm_list
z.feat.t.test.df <- bind_rows(z.feat.t.test, .id="perm") %>%
  mutate(pheno = sub(".z", "", pheno)) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

@@

```{r}
z.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=bigger_group)) +
  theme(axis.text.x = element_blank()) +
  facet_grid(pheno_cat~comp, scales="free_y", labeller = labeller(comp = as_labeller(comp_names)))
```

@@

ext_z.sum_raw <- ext_z.sum %>%
  dplyr::filter(dataset == "raw" & perm=="perm-001")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, gdata, gtExtras, webshot2)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")

@@

cent.tbl.pretty <- cent.tbl %>%
  mutate(comp = case_when(comp == "cf.gam_cf" ~ "ComBat-GAM vs ComBat w/o Covariates",
                          comp == "cf.gamlss_cf" ~ "ComBatLS vs ComBat w/o Covariates", 
                          comp == "cf.gamlss_cf.gam" ~ "ComBatLS vs ComBat-GAM",
                          comp == "cf.lm_cf" ~ "Linear ComBat vs ComBat w/o Covariates",
                          comp == "cf.lm_cf.gam" ~ "Linear ComBat vs ComBat-GAM",
                          comp == "cf.lm_cf.gamlss" ~ "Linear ComBat vs ComBatLS"),
         smaller_group = case_when(smaller_group == "cf" ~ "ComBat w/o Covariates",
                                   smaller_group == "cf.lm" ~ "Linear ComBat",
                                   smaller_group == "cf.gam" ~ "ComBat-GAM",
                                   smaller_group == "cf.gamlss" ~ "ComBatLS")) %>%
  rename(#"Pairwise Comparison"=comp,
         "Method Producing Smaller Absolute Errors" = smaller_group,
         "N Features" = n_sig,
         "% Features" = perc_tests)

pretty_cent_table <- cent.tbl.pretty %>%
  gt() %>% 
  #gt_theme_538() %>% 
tab_style(style = list(cell_fill(color = "gray95")),
    locations = cells_row_groups()) %>%
  fmt_percent(
    columns = "% Features",
    decimals = 2
  ) %>%
  tab_options(column_labels.font.weight = "bold") %>%
  tab_header(title = "Pairwise comparisons of ComBat methods' absolute centile errors for 208 brain features across 100 replications")

gtsave(pretty_cent_table, filename="figs/centile_table.png")
```

@@

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
cent.diffs.v.plot <- perm_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=dataset, y=mean_cent_abs.diff, color=perm), scale="count") +
  labs(y= "Mean Magnitude Centile Error", x = "ComBat Configurations") +
  scale_x_discrete(labels=c(dataset_names)) +
  # guides(fill=guide_legend(title="Sampling \nPermutation")) + 
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat configurations replicated 100x") +
  theme_linedraw() + 
  theme(legend.position="none")
cent.diffs.v.plot
ggsave(filename="figs/centile_violin.png", cent.diffs.v.plot, width=11, height=4.5, units="in")
```

@@

#look by feature type
sex_bias_hist_plt <- cent.subj.sex.test.df %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss" | dataset == "cf.lm") %>%
  mutate(dataset = factor(dataset, levels = c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    perm = as.factor(sub("perm-0", "", perm))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=perm, fill=perm), alpha=0.3, position="identity", bins=40) +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat ~ dataset, scales="free", labeller = labeller(dataset = as_labeller(dataset_names))) +
  theme_linedraw(base_size=12) +
  theme(legend.position = "none") +
  labs(x="Male - Female Median Centile Errors", y="Number of Features")
ggsave(filename="figs/sex_bias_hist_plt.png", sex_bias_hist_plt, height=7, width=10, units="in")
```

@@

t.test.cent.sex.test.med <- cent.sex.test.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 9.3,
                           dataset=="cf.lm" ~ 11,
                           dataset=="cf.gam" ~ 10.5,
                           dataset=="cf.gamlss" ~ 6))
#get vals
t.test.cent.sex.test.med

@@

sex_bias_density_plt <- cent.sex.test.med %>%
  dplyr::filter(dataset != "cf") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=y_pos),
              data = t.test.cent.sex.test.med.filt) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")

#with combat w/o covar
sex_bias_density_plt_full <- cent.sex.test.med %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=y_pos),
              data = t.test.cent.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom") +
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
ggsave(filename="figs/sex_bias_density_plt_full.png", sex_bias_density_plt_full, height=7, width=10, units="in")
```

@@

low_cent.sum <- perm_subj.df2_long %>%
  dplyr::filter(pheno_cat != "allpheno") %>%
  dplyr::filter(mean_centile < 0.20) %>%
  group_by(dataset, perm, pheno_cat) %>%
  summarise(
    male_ratio = sum(sex == "Male") / n(),
    female_ratio = sum(sex == "Female") / n()
  )
```

@@

@@

high_t_test.df <- lapply(split(high_cent.sum, high_cent.sum$pheno_cat), get_t_tests, raw_df=high_cent.sum_raw) %>% bind_rows()
low_t_test.df <- lapply(split(low_cent.sum, low_cent.sum$pheno_cat), get_t_tests, raw_df=low_cent.sum_raw) %>% bind_rows()

#merge dfs
all_cent_sum.df <- gdata::combine(high_cent.sum, low_cent.sum) %>%
  mutate(source = gsub("_cent.sum", "", source))
all_cent.sum_raw <- all_cent_sum.df %>%
  dplyr::filter(dataset == "raw" & perm=="perm-001")

all_t_test.df <- gdata::combine(high_t_test.df, low_t_test.df) %>%
  mutate(source = gsub("_t_test.df", "", source))

@@

all_t_test.df <- full_join(all_t_test.df, y_pos.df) %>%
  dplyr::filter(dataset != "raw")
```

```{r}
#plots!
all_cent_sum.df %>%
  dplyr::filter(dataset != "raw") %>%
  ggplot(aes(x=dataset, y=female_ratio)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y") +
  geom_hline(data=all_cent.sum_raw, aes(yintercept=female_ratio), linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = max_val + 0.01),
              data = all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"),  name = "ComBat Configuration", labels=dataset_names) + 
  theme_linedraw()

cent_ext_list <- c(high = ">80%", low = "<20%")

all_cent_sum_boxplt.diff <- all_cent_sum.df_scaled %>%
  dplyr::filter(dataset != "raw" & dataset != "cf") %>%
  mutate(source = factor(source, levels=c("low", "high", "ext"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio_diff)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(yintercept=0, linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = (y_pos)), nudge_y=.005,
               data = all_t_test.df[which(all_t_test.df$dataset != "cf"),]) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  # scale_y_continuous(labels=function(x)x/all_t_test.df$female_ratio[which(raw_df$pheno_cat == pheno_cat)]) + 
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Female Bias", x = "Dataset")

all_cent_sum_boxplt_wtest <- all_cent_sum.df %>%
  dplyr::filter(dataset != "raw") %>%
  mutate(source = factor(source, levels=c("low", "high"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="center") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=cent_ext_list)) +
  geom_hline(data=all_cent.sum_raw, aes(yintercept=female_ratio), linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = max_val + 0.01),
              data = all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Proportion Female", x = "Dataset")
#ggsave(filename="figs/all_cent_sum_boxplt_wtest.png", all_cent_sum_boxplt_wtest)
```

@@

```{r}
noext.cent.feat.t.test <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_t_tests_all_out.RDS"))
names(noext.cent.feat.t.test) <- n_perm_list
noext.cent.feat.t.test.df <- bind_rows(noext.cent.feat.t.test, .id="perm") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_))) %>%
      separate_wider_delim(cols=comp, delim="_", names=c("group1", "group2"), cols_remove=FALSE) %>%
  mutate(smaller_group=ifelse(bigger_group==group1, group2, group1))

@@

compare results
```{r}
noext.cent.t.test.df2 <- noext.cent.feat.t.test.df %>%
  mutate(full_df = "No Extremes")
cent.feat.t.test.df2 <- cent.feat.t.test.df %>%
  mutate(full_df = "Full Dataset")

@@

comp_names <- c(cf.gam_cf = "ComBat-GAM v. \nComBat w/o Covar", cf.gamlss_cf = "ComBatLS v. ComBat w/o Covar", cf.gamlss_cf.gam = "ComBatLS v. ComBat-GAM", cf.lm_cf.gam ="ComBat-GAM v. linear ComBat", cf.lm_cf.gamlss = "ComBatLS v. linear ComBat", cf.lm_cf = "linear ComBat v. \nComBat w/o Covar")
cent.test.comp.plt2 <- comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
  mutate(smaller_group=factor(smaller_group, levels=c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered=TRUE)) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=smaller_group)) +
  theme_linedraw()+
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "bottom") +
  facet_grid(comp ~ full_df, labeller = labeller(comp = as_labeller(comp_names))) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "Better ComBat \nConfiguration", labels=dataset_names) +
  labs(x="Sampling Permutation", y="Feature Count")
ggsave(filename="figs/cent_comp_noext.png", cent.test.comp.plt2, height=13, width=13, units="in")

@@

next.t.test.cent.sex.test.med <- noext.sex.testmed %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 6,
                           dataset=="cf.lm" ~ 9,
                           dataset=="cf.gam" ~ 9.5,
                           dataset=="cf.gamlss" ~ 5))

@@

sex_bias_density_plt_noext <- noext.sex.testmed %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=y_pos),
              data = next.t.test.cent.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
ggsave(filename="figs/sex_bias_density_plt_noext.png", sex_bias_density_plt_noext, height=7, width=10, units="in")
```

@@

```{r}
z.feat.t.test <- readRDS(paste0(data_path, "/full_featurewise_z_t_tests_all_out.RDS"))
names(z.feat.t.test) <- n_perm_list
z.feat.t.test.df <- bind_rows(z.feat.t.test, .id="perm") %>%
  mutate(pheno = sub(".z", "", pheno)) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_))) %>%
  separate_wider_delim(cols=comp, delim="_", names=c("group1", "group2"), cols_remove=FALSE) %>%
  mutate(smaller_group=ifelse(bigger_group==group1, group2, group1))

@@

z.feat.t.test.plt <- z.feat.t.test.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=perm, fill=smaller_group)) +
  theme_linedraw() + 
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "bottom") +
  labs(x="Sampling Permutation", y="Feature Count") +
  facet_grid(pheno_cat~comp, scales="free_y", labeller = labeller(comp = as_labeller(comp_names))) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "Better ComBat \nConfiguration", labels=dataset_names)

ggsave(filename="figs/z.feat.t.test.plt.png", z.feat.t.test.plt, height=7, width=13, units="in")
```

@@

z.high_t_test.df <- lapply(split(high_z.sum, high_z.sum$pheno_cat), get_t_tests, raw_df=high_z.sum_raw) %>% bind_rows()
z.low_t_test.df <- lapply(split(low_z.sum, low_z.sum$pheno_cat), get_t_tests, raw_df=low_z.sum_raw) %>% bind_rows()
